### 2021-09-03 input/proposal.tex
wip on theorem 8

\begin{theorem}[\label{theo:dcp}Purge + BEF $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When each \process can \texttt{Add} and \texttt{Del}ete its partition
at any time, consistent partitioning requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item and best eventual forwarding so such an $m'$ ends up originating from 
  the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  % As for CP, DCP requires that every process' last delivery

  \processes deliver and forward the best sum of weights they
  received. Figure~\ref{fig:proofA} depicts the generic case where a
  \process would block the epidemic propagation: the \process received
  and delivered a message from a partition that has since then been
  deleted but with a better sum of weights than newly received ones
  (in the example $\alpha_d^y < \alpha_a^{x'}$). Removing
  \emph{forever} all such stale messages about deleted partitions
  would allow \processes to propagate their best up-to-date partition
  again, eventually reaching consistent partitioning together, as
  stated by Theorem~\ref{theo:bef}.
\end{proof}

>>>>

\begin{theorem}[\label{theo:dcp}BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When a \process can \texttt{Add} and \texttt{Del}ete its partition,
consistent partitioning additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item then best eventual forwarding so such an $m'$ ends up
  originating from the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We need
  to prove that despite stale messages, the last delivery of every
  process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] Figure~\ref{fig:proofA} depicts the
    generic case where a \process $b$ precludes itself and subsequent
    \processes such as $c$ of delivering the message from their
    respective best source $a$. \Process $b$ received and delivered a
    message from a partition that has since then been deleted but with
    a better sum of weights than newly received ones ($\alpha_d^y <
    \alpha_a^{x'}$). It forever discards such a message
    $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:] Even assuming that every process
    immediately removes stale control information $S(\alpha_d^y)
    \implies d_b(\alpha_d^y) \rightarrow d_b(\delta_d)$, but received
    $\alpha^{x'}_a$ earlier $d_b(\alpha^{x'}_a) \rightarrow
    d_b(\alpha^y_d)$, it may never receive it again, hence staying
    with an empty state or another message that did not follow its
    shortest path to its best source.
  \item [Purge then BEF:] Removing \emph{forever} all such stale
    messages about deleted partitions would allow \processes to
    propagate their best up-to-date partition again, eventually
    reaching consistent partitioning together, as stated by
    Theorem~\ref{theo:bef}.
  \end{asparadesc}
\end{proof}
